Stat 400 Presentation

### 2021-12-08 Stat 400 presentation.Rmd
Created a good demonstration of simulator

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Starting Values Function

\tiny
```{r, echo=TRUE}
starting_vals <- function(num_subjects, I_0, x_dim, y_dim){

  return(df)
}
```

\tiny
```{r, echo = FALSE, output = TRUE}
library(ggplot2)
starting_vals <- function(num_subjects, I_0, x_dim, y_dim){

@@

@@

ggplot() +
  geom_line(aes(x=x, y=y)) +
  xlab('Day') +
  ylab('Number of Cases') +
  ggtitle('Number of Covid-19 cases over time')
```

>>>>

```{r}
library(tidyverse)
library(ggplot2)
library(boot)

starting_vals <- function(num_subjects, I_0, x_dim, y_dim){

@@

simulator22 <- function(days, num_subjects, x_dim, y_dim, I_0, inf_dist){
  initial_data <- starting_vals(num_subjects = num_subjects, x_dim=x_dim, y_dim=y_dim, I_0=I_0)
  end_day <- list()
  num_cases <- rep(NA, days)
  num_cases <- c(I_0, num_cases)
  num_new_cases <- rep(NA, days)

    }
  }
  return(end_day)
}
```

## Changing SIR Status

\tiny
```{r, echo=TRUE}
infection_status <- function(state, mean_crit_dist){

  newly_infected <- NULL

  if(nrow(current_suceptable) != 0 & nrow(current_infected) != 0){
  for(i in 1:nrow(current_infected)){
    for(j in 1:nrow(current_suceptable)){
      x_i <- as.numeric(current_infected[i, 'x'])
      y_i <- as.numeric(current_infected[i, 'y'])
      x_s <- as.numeric(current_suceptable[j, 'x'])
      y_s <- as.numeric(current_suceptable[j, 'y'])

      d <- sqrt((x_i - x_s)^2 + (y_i - y_s)^2)
      if(d <= crucial_distance){
        newly_infected <- c(newly_infected, j)
      }
    }
  }
  current_suceptable[newly_infected, 3] <- 'I'
  current_suceptable[newly_infected, 4] <- rpois(n=length(newly_infected), lambda = 5)
  current_suceptable[newly_infected, 5] <- rpois(n=length(newly_infected), lambda = 14)

  new_state <- rbind(current_infected, current_suceptable, current_removed, current_non_contagious)
  return(new_state)
  }else{return(state)}
}
```

## Simulation

\tiny
```{r, echo=TRUE}
dummy_simulator <- function(days, num_subjects, x_dim, y_dim, I_0, inf_dist){
  initial_data <- starting_vals(num_subjects = num_subjects, x_dim=x_dim, y_dim=y_dim, I_0=I_0)
  end_day <- list()
  num_cases <- rep(NA, days)
  num_cases <- c(I_0, num_cases)
  num_new_cases <- rep(NA, days)
  for(i in 1:days){
    if(i == 1){
      step_size <- get_step_length(initial_data, x_dim, y_dim)
      direction <- get_step_direction(step_size)
      change <- get_delts(step_size, direction)
      updated_positions <- update_coords(initial_data, change)
      checked_positions <- coord_checker(og_df=initial_data, new_df=updated_positions, x_dim=x_dim, y_dim=y_dim)
      new_status <- infection_status(checked_positions, inf_dist)

      not_recovered <- new_status[as.numeric(new_status[, 5]) > 0, ]
      new_time <- as.numeric(not_recovered[, 5]) - 1
      not_recovered[, 5] <- new_time
      infected_0 <- new_status[as.numeric(new_status[, 5]) == 0, ]
      infected_0[, 3] <- rep('R', nrow(infected_0))
      not_infected = new_status[as.numeric(new_status[, 5]) < 0, ]
      new_status = rbind(not_recovered, infected_0, not_infected)
      infected_people <- new_status[new_status[,3] == 'I',]
      new_inc_time <- as.numeric(infected_people[,4]) - 1
      infected_people[,4] <- new_inc_time
      other_people <- new_status[new_status[,3] != 'I',]
      new_status <- rbind(infected_people, other_people)
      end_day[[i]] <- new_status
      num_cases[i+1] <- sum(new_status[,3]=='I')
      num_new_cases[i] <- sum(new_status[,3]=='I') - I_0
    }
    }
  return(num_cases)
}
```

## Demonstration Day 1

```{r}
days <- simulator22(30, 10, 1, 1, 1, 0.2)

ggplot() +
  geom_point(aes(x=days[[1]][, 'x'], y= days[[1]][, 'y'], color=days[[1]][, 'subjects'])) +
  xlab('x position') +
  ylab('y position') +
  ggtitle('Infection Status and Position') +
  theme(axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank())

```

## Demonstration Day 5

```{r}
ggplot() +
  geom_point(aes(x=days[[5]][, 'x'], y= days[[5]][, 'y'], color=days[[5]][, 'subjects'])) +
  xlab('x position') +
  ylab('y position') +
  ggtitle('Infection Status and Position') +
  theme(axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank())

```

## Demonstration Day 10

```{r}
ggplot() +
  geom_point(aes(x=days[[10]][, 'x'], y= days[[10]][, 'y'], color=days[[10]][, 'subjects'])) +
  xlab('x position') +
  ylab('y position') +
  ggtitle('Infection Status and Position') +
  theme(axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank())

```

## Demonstration Day 15

```{r}
ggplot() +
  geom_point(aes(x=days[[15]][, 'x'], y= days[[15]][, 'y'], color=days[[15]][, 'subjects'])) +
  xlab('x position') +
  ylab('y position') +
  ggtitle('Infection Status and Position') +
  theme(axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank())

```

## Demonstration Day 20

```{r}
ggplot() +
  geom_point(aes(x=days[[20]][, 'x'], y= days[[20]][, 'y'], color=days[[20]][, 'subjects'])) +
  xlab('x position') +
  ylab('y position') +
  ggtitle('Infection Status and Position') +
  theme(axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank())

```

## Demonstration Day 25

```{r}
ggplot() +
  geom_point(aes(x=days[[25]][, 'x'], y= days[[25]][, 'y'], color=days[[25]][, 'subjects'])) +
  xlab('x position') +
  ylab('y position') +
  ggtitle('Infection Status and Position') +
  theme(axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank())

```

## Demonstration Day 30

```{r}
ggplot() +
  geom_point(aes(x=days[[30]][, 'x'], y= days[[30]][, 'y'], color=days[[30]][, 'subjects'])) +
  xlab('x position') +
  ylab('y position') +
  ggtitle('Infection Status and Position') +
  theme(axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank())

```

## Bootstrap Confidence Intervals

\tiny
```{r, echo=TRUE}
get_bootstrap_cis <- function(days, num_subjects, x_dim, y_dim, I_0, inf_dist, sample_size, ci_type='perc'){
  #Create data frame to store samples
  samps <- matrix(data=NA, nrow=sample_size, ncol=days + 1)
  samps <- data.frame(samps)

  #Create data frame to store confidence intervals
  ci_df <- matrix(data=NA, nrow=days + 1, ncol=3)
  ci_df <- data.frame(ci_df)

  for(i in 1:sample_size){
    samps[i, ] <- simulator(days, num_subjects, x_dim, y_dim, I_0, inf_dist)
  }

  for(i in 1:ncol(samps)){
    #Make sure column has more than one unique value
    check <- (length(unique(samps[ ,i])) != 1)
    if(check){
    boot_obj <- boot(samps[ ,i], mean_func, 2000)
    ci_obj <- boot.ci(boot_obj, conf = .95, type = ci_type)
    ci_df[i, 1] <- ci_obj$percent[4]
    ci_df[i, 2] <- ci_obj$t0
    ci_df[i, 3] <- ci_obj$percent[5]
    }else{ci_df[i, ] <- c(samps[1, i], samps[1, i], samps[1, i])}
  }
return(ci_df)
}
```

\tiny
```{r, echo = FALSE, output = TRUE}
library(ggplot2)

@@

y

ggplot() +
  geom_line(aes(x=x, y=y)) +
  xlab('Day') +
  ylab('Number of Cases') +
  ggtitle('Number of Covid-19 cases over time')

```
